Ice sheet mass flows

### 2025-06-23 sankey.tex
Remove bolded text from figures

    \newcommand\labelleft[1]{ % valname
      \node[font=\tiny, anchor=east]
      at ([yshift=0mm,xshift=-3mm]#1.center) {\Lab{v#1}: \qq{#1}};
    }
    \newcommand\labelright[2]{ % valname
      \node[font=\tiny, anchor=west]
      at ([yshift=0mm,xshift=3mm]#1.center) {\qq{#1}: \Lab{#2}};
    }
    \newcommand\labelbold[2]{ % valname
      \node[font=\tiny, anchor=west]
      at ([yshift=0mm,xshift=3mm]#1.center) {\textbf{\qq{#1}: \Lab{#2}}};
    }

@@

    \sankeyoutin[ice-to-water]{GZ}{GZa}; \sankeyadvance[water]{GZa}{10mm};
    \sankeyend[water]{GZa}; \labelbold{GZa}{vGZRET}
    \sankeyadvance[out-blue]{FRONTRETa}{10mm}; 
    \sankeyend[out-blue]{FRONTRETa}; \labelbold{FRONTRETa}{vFRONTRET}

@@

    \ifthenelse{\Q{vMG} < \Q{vML}} { % mass loss
      \sankeynode{name=ML, quantity=\Q{vML},
        at={[yshift=6mm]RF.north}, anchor=right, angle=-45}
      \node[font=\tiny, anchor=east]
      at ([xshift=-3mm,yshift=2mm]ML.west) {\textbf{Drawdown or retreat: \qq{ML}}};

>>>>

    \newcommand\labelleft[1]{ % valname
      \node[font=\tiny, anchor=east]
      at ([yshift=0mm,xshift=-3mm]#1.center) {\Lab{v#1}: \qq{#1}};
    }
    \newcommand\labelright[2]{ % valname
      \node[font=\tiny, anchor=west]
      at ([yshift=0mm,xshift=3mm]#1.center) {\qq{#1}: \Lab{#2}};
    }

@@

    \sankeyoutin[ice-to-water]{GZ}{GZa}; \sankeyadvance[water]{GZa}{10mm};
    \sankeyend[water]{GZa}; \labelright{GZa}{vGZRET}
    \sankeyadvance[out-blue]{FRONTRETa}{10mm}; 
    \sankeyend[out-blue]{FRONTRETa}; \labelright{FRONTRETa}{vFRONTRET}

@@

    \ifthenelse{\Q{vMG} < \Q{vML}} { % mass loss
      \sankeynode{name=ML, quantity=\Q{vML},
        at={[yshift=6mm]RF.north}, anchor=right, angle=-45}
      \node[font=\tiny, anchor=east]
      at ([xshift=-3mm,yshift=2mm]ML.west) {Drawdown or retreat: \qq{ML}};
